### 2020-03-05 short.body.tex
time for dinner

To begin, consider a SEIR model variant in which there are two infectious categories --
$I_a$ and $I_s$ -- corresponding to asymptomatic and symptomatic cases,
respectively. Both types of individuals can infect others, but,
only symptomatic cases can lead to fatalities, denoted
by the $D$ category. In total, the dynamics of susceptibles, exposed,
infectious, recovered, and dead are:
\begin{eqnarray}
\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
\dot{D}&=&f\gamma_s I_s.
\end{eqnarray}
Here, $\beta_a$ and $\beta_s$ denote transmission rates,
$\gamma_e$ denotes the transition from exposed to infectious,
$p$ is the fraction of asymptomatic cases that
are generated for each exposed individual,
$1-p$ is the fraction of symptomatic cases that
are generated for each exposed individual,
$\gamma_a$ and $\gamma_s$ denote recovery rates,
and $f$ denotes the case fatality ratio for symptomatic cases.

@@

The number of infected cases is expected
to increase exponentially at rate $r$ at the outset of an outbreak.  We note
that, in practice,
counted cases may largely be of the symptomatic type. 
Hence, we ask: is the expected ratio of $I_a/I_s$ 
during the outbreak phase the same or different
than $p/(1-p)$?  In other words, is the ratio of asymptomatic to symptomatic cases population-wide approximately equal to the ratio of asymptomatic to symptomatic cases generated by newly exposed individuals?
To answer this question, note that the equations
for the infectious cases can be rewritten given the ansatz
$E(t)=c_e e^{rt}$,
$I_a(t)=c_a e^{rt}$,
$I_s(t)=c_s e^{rt}$,
given the prefactors $c_e$, $c_a$, and $c_s$
such that
\begin{eqnarray}
r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
\end{eqnarray} 
which implies that
%\begin{eqnarray}
%c_a(r+\gamma_a)&=&p\gamma_e c_e,\\
%c_s(r+\gamma_s)&=&(1-p)\gamma_e c_e.
%\end{eqnarray} 
%Taking the ratio of these two equations yieldds
\begin{equation}
\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
\label{eq.relevance}
\end{equation}
%Alternatively, this same equation can be written as:
%\begin{equation}
%\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{1+\tau/T_s}{1+\tau/T_a}\right]
%\end{equation}
%where $\tau$ is the characteristic time of exponential case increase,
%$T_s$ is the average period of symptomatic infectious periods,
%and $T_a$ is the average period of asymptomatic infectious periods. 
Hence, we conclude that, during the exponential
growth phase, the intrinsic
ratio of asymptomatic to symptomatic cases ($p/(1-p)$) may differ from
the realized ratio at the population level ($c_a/c_s$).  
%This difference
%suggests that additional steps are required to link asymptomatic features
%at the individual to the population scale, i.e., by including
%the unknown transmission rates, $\beta_a$ and $\beta_s$.
Indeed, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
individuals during the exponential phase should be
\begin{equation}
\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
\label{eq.qratio}
\end{equation}
where $q$ is the fraction of new secondary cases caused by
asymptomatic individuals or `relevance' of asymptomatic cases.
The value of $q$ is an unknown feature of
outbreaks at the population scale, distinct from $p$ the probability of becoming
asymptomatic upon infection. 
As is apparent from Eq.~\req{eq.qratio}, relevance increases
with both $p$ and $\beta_a/\beta_s$. However, the consequences
for outbreak potential depends on the relative duration of infectiousness.

Here, given $1/r=7$ days, $1/\gamma_e=4$ days, and
$1/\gamma_s=10$ days, we evaluate the impacts of $p$ and $\beta_a/\beta_s$ on the
relevance of asymptomatic infections, given variation in 
$p$, $\beta_a/\beta_s$, and $\gamma_a$.  We consider two
scenarios, one in which asymptomatic infectiousness is short, i.e., with
average duration of $1/\gamma_a=5$ days,
and one in which asymptomatic infectiousness is long,i.e., $1/\gamma_a=20$ days.
We use the renewal equation formalism to explicitly link duration of infectiousness to the 
basic reproductive number (for technical details and example 
applications see~\citep{wallinga2007generation,weitz_scirep2015,champredon_2018}).
In brief, we
infer ${\cal{R}}_0$ compatible with an estimated value of $r$ from case
data given the generation interval distribution 
(set by $q$ and the duration in the exposed and infectious states).
By solving for $q$, we can then relate the basic
reproduction number to the relative transmission rates ($\beta_a/\beta_s$)
and the probability, $p$, of asymptomatic cases at the individual scale.
Figure~\ref{fig.relevance}C shows that
when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
with $q$. 
This increase arises because asymptomatic infections that resolve
slower increase the duration of
overall generation intervals (see~\citep{park_2019practical}). In contrast,
Figure~\ref{fig.relevance}D show that
when $\gamma_a>\gamma_s$ then
the strength ${\cal{R}}_0$ decreases with $q$.  
This decrease arises because asymptomatic infections that resolve
faster decrease the duration of
overall generation intervals (again, see~\citep{park_2019practical}). In both 
cases, the dependence of ${\cal{R}}_0$ on $q$ is
compared to a baseline of 
${\cal{R}}_0\approx 3.1$ in a model with no secondary
case production from asymptomatic infections (see filled
circle at bottom left of Figure~\ref{fig.relevance}C-D.
In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.

@@

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{group/figheatmap_seirdR0_noname.pdf}\\
\mbox{}\\
\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_2_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{group/figheatmap_seird_R02_noname.pdf}
\caption{Relevance of asymptomatic transmission given variation in
relative transmission and probability that a given, newly infected individual is asymptomatic.  (Top) Long duration asymptomatic cases increase ${\cal{R}}_0$ with increasing relevance.
(Bottom) Short duration asymptomatic cases decrease ${\cal{R}}_0$ with increasing relevance.
Technically, renewal equations provide a route to connect
observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
For the present model,
$M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
and $q$ is the fraction of realized new secondary cases caused by
asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
$\gamma_s=1/10$, and $r=1/7$. Here, the average duration
in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
$T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
$p=0.5$ and $p=0.9$ for reference.
%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and 
%$M(r)$ is related to 
%$g(a)$ (the normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. 
%The relevance $q$ is an unknown feature of
\label{fig.relevance}}
\end{center}
\end{figure*}

>>>>

To begin, consider a renewal equation variant in which incidence $i$ is divided into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively. 
Both types of individuals can infect others, but, they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$, reflecting their differences in the abilities to transmit and the courses of infection.
Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person, depend on the natural history of infection:
an individual with subclinical, and fast-clearing, symptoms is likely to have short generation intervals, whereas an individual with mild, but long-lasting, symptoms is likely to have long generation intervals.
In total, the dynamics of susceptibles and incidence are:
\begin{eqnarray}
\dot{S}&=&-i(t) \\
i(t)&=&\mathcal R_a S \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
\end{eqnarray}
Here, $p$ is the fraction of asymptomatic cases that are generated for each infected individual ($i_a(t)= p i(t)$), and $1-p$ is the fraction of symptomatic cases that are generated for each infected individual ($i_s(t)= (1-p) i(t)$).

%To begin, consider a SEIR model variant in which there are two infectious categories --
%$I_a$ and $I_s$ -- corresponding to asymptomatic and symptomatic cases,
%respectively. Both types of individuals can infect others, but,
%only symptomatic cases can lead to fatalities, denoted
%by the $D$ category. In total, the dynamics of susceptibles, exposed,
%infectious, recovered, and dead are:
%\begin{eqnarray}
%\dot{S}&=&-\beta_a S I_a -\beta_s S I_s \\
%\dot{E}&=&\beta_a S I_a +\beta_s S I_s -\gamma_e E\\
%\dot{I}_a&=&p\gamma_e E-\gamma_a I_a\\
%\dot{I}_s&=&(1-p)\gamma_e E-\gamma_s I_s\\
%\dot{R}&=&\gamma_a I_a + (1-f)\gamma_s I_s \\
%\dot{D}&=&f\gamma_s I_s.
%\end{eqnarray}
%Here, $\beta_a$ and $\beta_s$ denote transmission rates,
%$\gamma_e$ denotes the transition from exposed to infectious,
%$p$ is the fraction of asymptomatic cases that
%are generated for each exposed individual,
%$1-p$ is the fraction of symptomatic cases that
%are generated for each exposed individual,
%$\gamma_a$ and $\gamma_s$ denote recovery rates,
%and $f$ denotes the case fatality ratio for symptomatic cases.

The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s.
\end{equation}
Then, the \emph{intrinsic} proportion of asymptomatic $z$ and symptomatic $1-z$ transmission is equal to their relative contribution toward the basic reproduction number, 
\begin{eqnarray}
z &=& p {\cal{R}}_a/{\cal{R}}_{0},\\
1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
\end{eqnarray}
Then, the \emph{intrinsic} generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding \emph{intrinsic} generation-interval distributions:
\begin{equation}
g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
\end{equation}
which allows us to express incidence of infection as a renewal process that depends on previous incidence:
\begin{equation}
i(t) = {\cal{R}}_{0} \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
\end{equation}
Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?

The number of infected cases is expected to increase exponentially at rate $r$ at the outset of an outbreak. We note that, in practice, counted cases may largely be of the symptomatic type. 
Hence, we ask: is the expected ratio of incidence caused by asymptomatic cases vs.~symptomatic cases during the outbreak phase the same or different than $z/(1-z)$?
The ratio of secondary case production caused by asymptomatic vs.~symptomatic individuals during the exponential phase should be
\begin{equation}
\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right],
\label{eq.qratio}
\end{equation}
where $q$ is the fraction of new secondary cases caused by asymptomatic individuals or `relevance' of asymptomatic cases. 
The value of $q$ is an unknown feature of outbreaks at the population scale, distinct from $p$ the probability of becoming asymptomatic upon infection or $z$ the intrinsic proportion of asymptomatic transmission.

Assuming that the intrinsic generation-interval distributions for asymptomatic and symptomatic cases follow gamma distributions with different means, $\bar G_a$ and  $\bar G_s$, and dispersions (represented by squared coefficients of variations), $\kappa_a$ and $\kappa_s$. 
Then, we have
\begin{equation}
\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{(1 + \kappa_s r \bar G_s)^{1/\kappa_s}}{(1 + \kappa_a r \bar G_a)^{1/\kappa_a}}\right].
\label{eq.gammaratio}
\end{equation}
As is apparent from Eq.~\req{eq.qratio}, relevance $q$ increases with $z$, i.e., with both $p$ and $\mathcal R_a/\mathcal R_s$. The consequences for outbreak potential further depends on the relative lengths of generation intervals as well as the relative amount of dispersions in them.

@@

%The number of infected cases is expected
%to increase exponentially at rate $r$ at the outset of an outbreak.  We note
%that, in practice,
%counted cases may largely be of the symptomatic type. 
%Hence, we ask: is the expected ratio of $I_a/I_s$ 
%during the outbreak phase the same or different
%than $p/(1-p)$?  In other words, is the ratio of asymptomatic to symptomatic cases population-wide approximately equal to the ratio of asymptomatic to symptomatic cases generated by newly exposed individuals?
%To answer this question, note that the equations
%for the infectious cases can be rewritten given the ansatz
%$E(t)=c_e e^{rt}$,
%$I_a(t)=c_a e^{rt}$,
%$I_s(t)=c_s e^{rt}$,
%given the prefactors $c_e$, $c_a$, and $c_s$
%such that
%\begin{eqnarray}
%r c_a&=&p\gamma_e c_e-\gamma_a c_a,\\
%r c_s&=&(1-p)\gamma_e c_e-\gamma_s c_s,
%\end{eqnarray} 
%which implies that
%\begin{eqnarray}
%c_a(r+\gamma_a)&=&p\gamma_e c_e,\\
%c_s(r+\gamma_s)&=&(1-p)\gamma_e c_e.
%\end{eqnarray} 
%Taking the ratio of these two equations yieldds
%\begin{equation}
%\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right].
%\label{eq.relevance}
%\end{equation}
%Alternatively, this same equation can be written as:
%\begin{equation}
%\frac{c_a}{c_s}=\frac{p}{1-p}\left[\frac{1+\tau/T_s}{1+\tau/T_a}\right]
%\end{equation}
%where $\tau$ is the characteristic time of exponential case increase,
%$T_s$ is the average period of symptomatic infectious periods,
%and $T_a$ is the average period of asymptomatic infectious periods. 
%Hence, we conclude that, during the exponential
%growth phase, the intrinsic
%ratio of asymptomatic to symptomatic cases ($p/(1-p)$) may differ from
%the realized ratio at the population level ($c_a/c_s$).  
%%This difference
%suggests that additional steps are required to link asymptomatic features
%at the individual to the population scale, i.e., by including
%the unknown transmission rates, $\beta_a$ and $\beta_s$.
%Indeed, the ratio of secondary case production caused by asymptomatic vs.~symptomatic
%individuals during the exponential phase should be
%\begin{equation}
%\frac{q}{1-q} = \left(\frac{\beta_a}{\beta_s}\right)\frac{p}{1-p}\left[\frac{r+\gamma_s}{r+\gamma_a}\right],
%\label{eq.qratio}
%\end{equation}
%where $q$ is the fraction of new secondary cases caused by
%asymptomatic individuals or `relevance' of asymptomatic cases.
%The value of $q$ is an unknown feature of
%outbreaks at the population scale, distinct from $p$ the probability of becoming
%asymptomatic upon infection. 
%As is apparent from Eq.~\req{eq.qratio}, relevance increases
%with both $p$ and $\beta_a/\beta_s$. However, the consequences
%for outbreak potential depends on the relative duration of infectiousness.

Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ from 0.5 to 1.5, one at a time, and infer $q$ as well as ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (thus, faster infection) drive transmission events during the growth phase.
On the other hand, assuming a wider asymptomatic generation interval (higher $\kappa_a$) increases $q$ because

Figure~\ref{fig.relevance}C shows that
when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
with $q$. 
This increase arises because asymptomatic infections that resolve
slower increase the duration of
overall generation intervals (see~\citep{park_2019practical}). In contrast,
Figure~\ref{fig.relevance}D show that
when $\gamma_a>\gamma_s$ then
the strength ${\cal{R}}_0$ decreases with $q$.  
This decrease arises because asymptomatic infections that resolve
faster decrease the duration of
overall generation intervals (again, see~\citep{park_2019practical}). In both 
cases, the dependence of ${\cal{R}}_0$ on $q$ is
compared to a baseline of 
${\cal{R}}_0\approx 3.1$ in a model with no secondary
case production from asymptomatic infections (see filled
circle at bottom left of Figure~\ref{fig.relevance}C-D.
In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.

%Here, given $1/r=7$ days, $1/\gamma_e=4$ days, and
%$1/\gamma_s=10$ days, we evaluate the impacts of $p$ and $\beta_a/\beta_s$ on the
%relevance of asymptomatic infections, given variation in 
%$p$, $\beta_a/\beta_s$, and $\gamma_a$.  We consider two
%scenarios, one in which asymptomatic infectiousness is short, i.e., with
%average duration of $1/\gamma_a=5$ days,
%and one in which asymptomatic infectiousness is long,i.e., $1/\gamma_a=20$ days.
%We use the renewal equation formalism to explicitly link duration of infectiousness to the 
%basic reproductive number (for technical details and example 
%applications see~\citep{wallinga2007generation,weitz_scirep2015,champredon_2018}).
%In brief, we
%infer ${\cal{R}}_0$ compatible with an estimated value of $r$ from case
%data given the generation interval distribution 
%(set by $q$ and the duration in the exposed and infectious states).
%By solving for $q$, we can then relate the basic
%reproduction number to the relative transmission rates ($\beta_a/\beta_s$)
%and the probability, $p$, of asymptomatic cases at the individual scale.
%Figure~\ref{fig.relevance}C shows that
%when $\gamma_a<\gamma_s$, then the strength ${\cal{R}}_0$ increases
%with $q$. 
%This increase arises because asymptomatic infections that resolve
%slower increase the duration of
%overall generation intervals (see~\citep{park_2019practical}). In contrast,
%Figure~\ref{fig.relevance}D show that
%when $\gamma_a>\gamma_s$ then
%the strength ${\cal{R}}_0$ decreases with $q$.  
%This decrease arises because asymptomatic infections that resolve
%faster decrease the duration of
%overall generation intervals (again, see~\citep{park_2019practical}). In both 
%cases, the dependence of ${\cal{R}}_0$ on $q$ is
%compared to a baseline of 
%${\cal{R}}_0\approx 3.1$ in a model with no secondary
%case production from asymptomatic infections (see filled
%circle at bottom left of Figure~\ref{fig.relevance}C-D.
%In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.

@@

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}\\
\mbox{}\\
\includegraphics[width=0.4\textwidth]{figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_kappa_R0.pdf}
\caption{Relevance of asymptomatic transmission given variation in
relative transmission and probability that a given, newly infected individual is asymptomatic.  (Top) Long duration asymptomatic cases increase ${\cal{R}}_0$ with increasing relevance.
(Bottom) Short duration asymptomatic cases decrease ${\cal{R}}_0$ with increasing relevance.
Technically, renewal equations provide a route to connect
observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
For the present model,
$M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
and $q$ is the fraction of realized new secondary cases caused by
asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
$\gamma_s=1/10$, and $r=1/7$. Here, the average duration
in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
$T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
$p=0.5$ and $p=0.9$ for reference.
%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and 
%$M(r)$ is related to 
%$g(a)$ (the normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. 
%The relevance $q$ is an unknown feature of
\label{fig.relevance}}
\end{center}
\end{figure*}
